Exploring the Usefulness of Varactor loaded Nonlinear Transmission Lines

### 2020-06-03 RohdeAndSchwarzWhitePaper/Draft_White_Paper.tex
added board characterization section and additional resources in bib.

First, we discuss the necessity of non-linear components in such a Nonlinear
Transmission line or NLTL for short. We then discuss ways in which the devices
we use in simulation are modeled and the obstacles we faced in constructing
these models. We simulate these nonlinear lines using MICROCAP and discuss
possible reasons for the discrepancies we have seen between research and
simulations.

@@

@@

%\subsection{Modeling Board Characteristics}

>>>>

First, we discuss the necessity of non-linear components in such a Nonlinear
Transmission line or \emph{NLTL} for short. We then discuss ways in which the
devices we use in simulation are modeled and the obstacles we faced in constructing
these models. We simulate these nonlinear lines using MICROCAP and discuss
possible reasons for the discrepancies we have seen between research and
simulations.

@@

\subsection{Modeling Board Characteristics}

When constructing a test fixture for measurements of NLTL's of higher frequency,
we must also take into account the properties of the board we are working with.
For our low frequency model and with limited access to robust VNA's this
procedure was not neccessary but we recommend using the two-line pencil
method to approximate the board permittivity and loss tangent as utilized to do
the same for flex PCB's due to it's simplicity and limited need for
equipment\cite{TwoLine}.

For our board, we used a simpler method which may prove useful as a quick and
dirty alternative to the one descbribed above. To find the permitivittivy of the
board we used a simple LCR Meter (DE-5000) and the following formula of a
parallel plate capacitor as shown in equation \ref{eq:epsAOverD}.

\begin{equation}\label{eq:epsAOverD}
	C =\frac{ \epsilon{}A }{d}
\end{equation}

Where we treat the width of the dielectric as plate spacing d, the board area
as area, A, and measured capacitance as C. Solving for Permittivity
$\epsilon$, we found a relative permittivity of $\epsilon_{r}\approx 3.54$.
For this measurement a figure normally given for FR4 is roughly 4.0 to 4.4. A
few possible things could cause this error.

The device used to measure the FR4 board generates a test frequency of 100kHz at
maximum. Relative permittivity is usually given for FR4 at a much higher
frequency in the Mhz range. Another is the precision achievable when measuring
the dielectric thickness. A caliper would be much better suited for this task.
Alternative methods do exist and are quite simple but do necessitate access to a
VNA\cite{SimpleRelative}.

@@
